\documentclass[bachelor,zhspacing]{cqu}  %单面打印版本
\usepackage{etex}
\def\tightlist{}

%%在这增加你需要的其它包
\definecolor{hellgelb}{rgb}{1,1,0.8}
\definecolor{colKeys}{rgb}{0,0,1}
\definecolor{colIdentifier}{rgb}{0,0,0}
\definecolor{colComments}{rgb}{1,0,0}
\definecolor{colString}{rgb}{0,0.5,0}
\usepackage{listings}
\lstset{%
    float=hbp,%
    basicstyle=\ttfamily\small, %
    identifierstyle=\color{colIdentifier}, %
    keywordstyle=\color{colKeys}, %
    stringstyle=\color{colString}, %
    commentstyle=\color{colComments}, %
    columns=flexible, %
    tabsize=4, %
    frame=single, %
    extendedchars=true, %
    showspaces=false, %
    showstringspaces=false, %
    numbers=left, %
    numberstyle=\tiny, %
    breaklines=true, %
   backgroundcolor=\color{hellgelb}, %
    breakautoindent=true, %
    captionpos=b,%
	xleftmargin=0pt%
}

\begin{document}

%-----------------------------------论文题目-------------------------------------------------
\xuehao{20121886}
\cntitle{基于卷积神经网络的人脸识别}
\cnauthor{李贝贝}
\cnmajor{软件工程}
\cnteacher{葛永新}
\cnxueyuan{软件学院}
\entitle{Face Recognization based on Convolutional Neural Network}
\enauthor{Beibei Li}
\enmajor{Software Engineering}
\enteacher{Prof. Yongxin Ge}
\enxueyuan{College of Software}
\cnkind{****}
\enkind{****}
%\cnzlteacher{ }  %%助理教师，如果必要，还要将cqu.cls中的有关该项前的%号去掉
%\enzlteacher{ }
\cndate{二O一六年六月}
\endate{June 2016}
%%%%只需修改上面的相关信息%%%%%%%%
\makecntitle 
\makeentitle 
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagenumbering{Roman}
\setcounter{page}{0}
%------------------------------------文章摘要------------------------------------------------------------
\cnkeywords{卷积神经网络，人脸识别，深度学习 }
\begin{cnabstract}

卷积神经网络在提出时就凭借其出色的性能吸引了很多学者的兴趣，与深度学习理论结合，使之再次成为研究热点。
卷积神经网络引入了稀疏局部连接、权值共享和子采样的思想，与多层感知器相比大大降低了需要训练参数的数量。
而且在空间上其具有一定的平移、扭曲不变性。目前，卷积神经网络被广泛用到模式识别的各个领域。\par

人脸识别是模式识别领域一直以来的热点和重难点，采用卷积神经网络进行人脸识别可以突破传统识别方法的瓶颈，具有重要的意义和价值。\par

本文旨在将卷积神经网络应用于人脸识别，围绕此目标，主要做了如下工作：

1.  总结和理解了感知器、多层感知器、梯度递减、后向传播等神经网络基础知识，学习卷积神经网络的主要思想和特点，理解其优越性。\par
2.  将卷积神经网络用于人脸识别问题并将结果与其他识别方法对比分析。最终卷积神经网络以96.63\%的正确率超过其它方法，并远远超过传统方法。\par
3.  分别使用卷积神经网络和传统特征提取方法对人脸数据进行特征提取并通过实验做比较分析。通过卷积神经网络的特征表现出更好的性能。

\end{cnabstract} 
\enkeywords{convolutional neural network , face recognition, deep learning}
\begin{enabstract}

Convolutional neural network attracted the interest of many scholars when it's proposed due to the excellent performence. Combining with deep learning, it become a hot topic once again. 
Convolutional neural network involved the idea of spatially-local correlation, shared weights and sampling, reducing the number of parameters to be trained comparing with multilayer perceptron. Besides, it has an advantage of translation, distorion invariance. Convolution neural network is widely used in various fields for pattern recognition.\par

Face recognition has been a hot, important and difficult spot in the field of pattern recognition. With the help of convolutional neural network, the bottleneck of traditional identification methods can be broken, which is significant and meaningful.\par

This paper aims to apply convolutional neural network to face recognition. And the following work was done:

1. Summary and understanding of perception, Multilayer Perceptron, gradient descent, backward propagation neural network and other basics, learn the main ideas and features of convolutional neural network and understand its advantages.\par

2. Do face recognition with convolutional neural network and some traditional methods, then make a comparison and analysis. And convolutional neural network is better than other methods with an accuracy rate of 96.63\%, and far better than traditional methods.\par

3. Extracting features through convolution neural network, and make comparison and analysis with features extracted by other traditional methods. And features extracted by convolutional neural network showed better performance. 
     
\end{enabstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%--------------文章目录-------------
\tableofcontents
\listoffigures
%\addcontentsline{toc}{section}{插图清单}
\listoftables
%\addcontentsline{toc}{section}{附表清单}


%------------------------------------词汇------------------------------------------------------------
\begin{denotation}{2.5}{0}

\item[w] 权值向量
\item[b] 偏移量
\end{denotation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagenumbering{arabic}

$body$

%\include{chapters/summery}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%\include{chapters/appendix}  %%附录

\end{document}
